\documentclass[11pt,aspectratio=169]{beamer}

\usetheme{default}
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{headline}{}
\setbeamertemplate{footline}[frame number]
\setbeamerfont{frametitle}{size=\large,series=\bfseries}

\usepackage{booktabs}
\usepackage{array}
\usepackage{xcolor}

\definecolor{qblue}{RGB}{30,80,160}
\definecolor{qlight}{RGB}{235,242,252}
\setbeamercolor{block title}{bg=qblue,fg=white}
\setbeamercolor{block body}{bg=qlight,fg=black}

\title{BDM Belief Elicitation and Behavioral Incentive Compatibility}
\subtitle{Design review}
\author{Christina Sun}
\date{April 2026}

\begin{document}

\begin{frame}[plain]
\maketitle
\end{frame}

\begin{frame}{Literature}
Danz, Vesterlund, and Wilson (JEP 2024 and forthcoming WP) mentions BDM fails BIC in pure incentive test: 69\% of subjects pick $q = 0$ under p-BDM at induced $\theta = 0.2$. No public WP available.

\vspace{0.6em}
Chakraborty and Kendall (2025) formalize UJS. BDM admits many justifiable non-truthful reports; MPL admits one, may be better BIC.

\end{frame}

\begin{frame}{Research questions and contribution}
Research questions:
\begin{enumerate}
\item Why does BDM belief elicitation fail behavioral IC?
\item Does MPL perform better, despite theoretical equivalence?
\item Does the presentation format interact with task complexity for belief elicitation?
\end{enumerate}

\vspace{0.8em}
Contribution: identify the mechanism behind BDM's failure, test UJS's design implication empirically in belief elicitation, and measure the complexity-by-mechanism interaction. 
\end{frame}

\begin{frame}{Theoretical IC: 2 Approaches}
    \begin{itemize}
        \item Karni (2009): Dominance + Probabilistic Sophistication
        \item Azrieli et al.\ (2018): Monotonicity
    \end{itemize}

    \vspace{0.5em}
    Azrieli's monotonicity is strictly weaker --- the minimal sufficient assumption for IC.
\end{frame}

\begin{frame}{Hypotheses}
\begin{description}
\item[H1.] BDM fails behavioral IC, via two weak conditions (DVW 2022):
\begin{itemize}
\item[H1a.] Explaining BDM's incentives does not increase accuracy.
\item[H1b.] Subjects do not choose the payoff-maximizer under pure incentives.
\end{itemize}
\item[H2.] Belief MPL achieves better behavioral IC than single-report BDM, despite theoretical equivalence, because MPL admits a unique justifiable action per row (UJS) while BDM admits many.
\item[H3.] The BDM-MPL truthful reporting gap increases with task complexity.
\end{description}
\end{frame}

\begin{frame}{Experimental design}
Ball and urn paradigm.
\vspace{0.7em}
\footnotesize
\setlength{\tabcolsep}{4pt}
\begin{tabular}{@{}p{0.03\linewidth} p{0.22\linewidth} p{0.32\linewidth} p{0.33\linewidth}@{}}
\toprule
T\# & Mechanism & Instructions & Identifies \\
\midrule
1 & Single-report BDM & Full info + quiz & H1 baseline \\
2 & Belief MPL & Full info + quiz & H2, format matters \\
3 & Single-report BDM & No info & H1a: info/no-info \\
4 & Pure-incentives test & --- & H1b: direct test \\
5 & Flat fee & Accuracy encouragement & No-mechanism benchmark \\
\bottomrule
\end{tabular}

\vspace{0.7em}
\small
Within-subject: priors (easy) and posteriors after signals (hard). Identifies H3.

Outcomes: Accuracy at $\varepsilon = 0$ and $\varepsilon = 5$pp (DVW 2022). Also multi-switching, response time, comprehension.

\end{frame}

\begin{frame}{Question 1: the overall design}
\begin{block}{}
Is there anything I am missing?
\end{block}

\vspace{1em}
\begin{itemize}
\item Is the current design sufficient to identify H1 through H3?
\item How to design p-BDM pure incentive test? (coming up next)
\item Other considerations?
\end{itemize}
\end{frame}

\begin{frame}{p-BDM pure-incentives test (H1b)}
DVW report one p-BDM pure incentive test result: 69\% of subjects pick $q = 0$ at $\theta = 0.2$. WP is not available.

\vspace{0.7em}
\begin{itemize}
\item $q = 0$ pays with probability $0.5$ regardless of event.
\item $q = \theta = 0.2$ (the maximizer) pays with probability $0.68$ if $E$, $0.48$ otherwise, for an expected $0.52$.
\item The EV gap between the maximizer and the event-independent option is 2 percentage points.
\end{itemize}


\end{frame}

\begin{frame}{Proposal A: Example at $\theta = 0.2$}
\small
$P(\text{win} \mid E, q) = q + (1 - q^2)/2$, \quad $P(\text{win} \mid \lnot E, q) = (1 - q^2)/2$.

\vspace{0.5em}
\footnotesize
\begin{tabular}{@{}c c c c l@{}}
\toprule
Report $q$ & $P(\text{win} \mid E)$ & $P(\text{win} \mid \lnot E)$ & EV & \\
\midrule
0.0 & 0.500 & 0.500 & 0.500 & event-independent \\
0.1 & 0.595 & 0.495 & 0.515 & \\
0.2 & 0.680 & 0.480 & 0.520 & maximizer, $q^* = \theta$ \\
0.3 & 0.755 & 0.455 & 0.515 & \\
0.4 & 0.820 & 0.420 & 0.500 & \\
0.5 & 0.875 & 0.375 & 0.475 & \\
0.6 & 0.920 & 0.320 & 0.440 & \\
0.7 & 0.955 & 0.255 & 0.395 & \\
0.8 & 0.980 & 0.180 & 0.340 & \\
0.9 & 0.995 & 0.095 & 0.275 & \\
1.0 & 1.000 & 0.000 & 0.200 & \\
\bottomrule
\end{tabular}

\vspace{0.3em}
\footnotesize
Mechanism and $q$ values hidden. Subject compares event-contingent payoff pairs directly --- no contingent reasoning across $r$ is required.
\end{frame}

\begin{frame}{Proposal B: Example at $\theta = 0.2$}
Urn: 20 red balls, 80 blue. Event $E$ = red drawn. $P(E) = 0.2 = \theta$.

\vspace{0.6em}
Subject sees:

\vspace{0.3em}
\begin{quote}
You will choose a number $q$ from $\{0.0, 0.1, 0.2, \ldots, 1.0\}$. A random $r$ is drawn uniformly from $[0, 1]$.
\begin{itemize}
\item If $q \geq r$: you win \$$H$ if red.
\item If $q < r$: you win \$$H$ with probability $r$.
\end{itemize}
Which $q$ do you pick?
\end{quote}

\vspace{0.3em}
\footnotesize
No payoff pairs shown. To find the maximizer, the subject must reason through what happens at each $r$ given each candidate $q$ --- full contingent reasoning demand preserved.
\end{frame}

\begin{frame}{Question 2: A, B, or both?}
The pure-incentives test diagnoses BIC failure by asking whether subjects identify the payoff-maximizer with beliefs stripped from the task.

\vspace{0.6em}
A and B differ in how much of the p-BDM structure remains:
\begin{itemize}
\item A: mechanism hidden; subjects see only event-contingent payoff pairs.
\item B: native p-BDM framing; contingent reasoning across $r$ preserved.
\end{itemize}

\vspace{0.4em}
Both designs are separate between-subject arms, with $\theta$ varying within-subject. Running A and B within-subject isolates menu-level vs. contingent-reasoning failure.

\vspace{0.6em}
\begin{block}{}
A, B, or something else?
\end{block}
\end{frame}

% <!-- primary-source-ok: segal_1990 -->
\begin{frame}{MPL format: the problem}
Brown and Healy (2018): MPL is theoretically IC, but presentation format determines whether it holds in practice.

\vspace{0.7em}
How list format can break IC:
\begin{enumerate}
\item All rows visible on one screen $\Rightarrow$ compound RPS structure is salient.
\item Subjects treat the list as one decision; apply ROCL.
\item ROCL $+$ non-EU preferences $\Rightarrow$ monotonicity violation (Segal 1990).
\item Monotonicity violated $\Rightarrow$ RPS no longer IC (Azrieli et al. 2018).
\end{enumerate}

\vspace{0.6em}
Fix: Separated format (one row per screen, random order): ROCL not triggered.
\end{frame}

\begin{frame}{MPL format: options and tradeoffs}

\vspace{0.6em}
\small
\setlength{\tabcolsep}{4pt}
\begin{tabular}{@{}p{0.30\linewidth} p{0.10\linewidth} p{0.17\linewidth} p{0.14\linewidth} p{0.12\linewidth}@{}}
\toprule
Format & Screens & ROCL concern & Burden & Precision \\
\midrule
Full list (all rows on 1 screen) & 1 & Yes & High & 1pp \\
Two-stage list (Holt \& Smith) & 2 & Yes & Moderate & 1pp \\
Full separated (100 rows) & 100 & No & High & 1pp \\
Coarse separated & 15--20 & No & Moderate & 5pp \\
Two-stage separated & 20--30 & No & High & 1pp \\
\bottomrule
\end{tabular}


\end{frame}

\begin{frame}{Two-stage formats: the Multiple Switching dilemma}
Two-stage MPL encounters a problem with how to handle multiple switching (MS):

\vspace{0.5em}
\begin{itemize}
\item \textbf{Force single-switching in Stage 1.} Stage 2 implementable, but censors MS behavior.
\item \textbf{Allow MS in Stage 1.} Stage 2 not implementable.
\item \textbf{Skip Stage 2 for MS subjects.} Asymmetric rounds across subjects.
\end{itemize}

\vspace{0.5em}
\footnotesize
Applies to two-stage list and two-stage separated.
\end{frame}

\begin{frame}{Question 3: MPL format}
Proposal: coarse separated (15--20 rows, one per screen, random order) --- the belief analog of UJS-E. 

Pro: Works for our BIC test at 5pp precision

Con: does not generalize to precision-sensitive belief elicitation.

\vspace{0.5em}
\begin{block}{}
How to approach MPL format choice?
\end{block}

\end{frame}

\end{document}
